---
title: "Plot plasma androgen levels and do stats"
output: html_notebook
author: "MaggieMCKO"
date: "12/25/2020"
---

This [R Markdown](http://rmarkdown.rstudio.com) Notebook contain codes for reproducing Fig.S1 of the [sex difference manuscript] ().


```{r}

library(tidyverse) # v.1.3.0

## load data
path =  paste0(getwd(), "/data/Plasma_androgen_conc.csv")
Testo = read_csv(path)

Testo$Group = factor(Testo$Group, 
                           levels = c("LDm", "SDm", "LDf", "SDf", "SDmT", "SDfT", "SDfS" ))
Testo$Facet = factor(Testo$Facet, levels = c("Breeding", "Non-breeding", "+ T"))

# plot
w = 0.2
TESTOb_post = ggplot(Testo, aes(y = Testo..ng.ml., x = Group)) + 
  geom_boxplot(outlier.colour = 'white', outlier.size = 0.5, width = 0.2,
               size = 0.3) + 
  geom_point(aes(color = Sex), position = position_nudge(x = w), size = 0.5) +
  scale_color_manual(values = c("mediumpurple1", "dodgerblue1")) +
  facet_grid(. ~ Facet, scales = "free", space = "free") +
  scale_y_log10(name = 'Plasma androgens (ng/ml)') +
  theme(panel.background = element_blank(),
        plot.background = element_blank(), 
        plot.title =  element_blank(), 
        panel.border =  element_blank(), 
        panel.grid = element_blank(),
        axis.line = element_line(color = "black", size = .2),
        axis.title.x = element_blank(),
        axis.ticks = element_line(colour = "black", size = 0.05),
        strip.text = element_text(margin = margin(1,1,1,1, unit = 'pt') ),
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(colour = "black", size = 5),
        legend.position = c(0.9, 0.2)); TESTOb_post

```
# Mann-Whitney Test
### 1. Breeding canay males vs females
```{r}
tmp = Testo %>% filter(Facet == 'Breeding')
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Sex , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Sex) %>% summarise(mean = mean(Testo..ng.ml.))

pval_LDm_LDf = w$p.value

```
### 2. Non-breeding males vs non-breeding non-singing females
```{r}
tmp = Testo %>% filter(grepl("SDm$|SDf$", Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Sex , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Sex) %>% summarise(mean = mean(Testo..ng.ml.))

pval_SDm_SDf = w$p.value
```


### 3. Non-breeding males vs non-breeding singing females
```{r}
tmp = Testo %>% filter(grepl("SDm$|SDfS$", Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Sex , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Sex) %>% summarise(mean = mean(Testo..ng.ml.))

pval_SDm_SDfS = w$p.value

```

### 4. Testosterone-implanted males vs testosterone-implanted females
```{r}
tmp = Testo %>% filter(Facet == '+ T')
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Sex , data = tmp, alternative = "two.sided")
print(w)
# cal mean 
tmp %>% group_by(Sex) %>% summarise(mean = mean(Testo..ng.ml.))

pval_SDmT_SDfT = w$p.value

```

### 5. Testosterone-implanted males vs non-breeding non-singinge males
```{r}
tmp = Testo %>% filter(grepl('SDm$|SDmT$', Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Group , data = tmp, alternative = "two.sided")
print(w)
# cal mean 
tmp %>% group_by(Group) %>% summarise(mean = mean(Testo..ng.ml.))

pval_SDmT_SDm = w$p.value

```

### 6. Testosterone-implanted females vs non-breeding non-singinge females
```{r}
tmp = Testo %>% filter(grepl('SDf$|SDfT$', Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Group , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Group) %>% summarise(mean = mean(Testo..ng.ml.))

pval_SDfT_SDf = w$p.value

```

### 7. Breeding males vs testosterone-implanted males
```{r}
tmp = Testo %>% filter(grepl('LDm$|SDmT$', Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Group , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Group) %>% summarise(mean = mean(Testo..ng.ml.))

pval_LDm_SDmT = w$p.value

```


### 8. Breeding males vs non-breeding non-singing males
```{r}
tmp = Testo %>% filter(grepl('LDm$|SDm$', Group))
# head(tmp)

# Mann-Whitney Test
w = wilcox.test(Testo..ng.ml. ~ Group , data = tmp, alternative = "two.sided")
print(w)

# cal mean 
tmp %>% group_by(Group) %>% summarise(mean = mean(Testo..ng.ml.))

pval_LDm_SDm = w$p.value

```

### adjusted p values
```{r}
pvals = c("pval_LDm_LDf" = pval_LDm_LDf, 
          "pval_SDm_SDf" = pval_SDm_SDf, "pval_SDm_SDfS" = pval_SDm_SDfS, 
          "pval_SDmT_SDfT" = pval_SDmT_SDfT, 
          "pval_SDmT_SDm" = pval_SDmT_SDm, "pval_SDfT_SDf" = pval_SDfT_SDf,
          "pval_LDm_SDm" = pval_LDm_SDm, "pval_LDm_SDmT"= pval_LDm_SDmT
          )


padj = p.adjust(pvals, "bonferroni")

df = data.frame(pvals, padj)
print(df)
```

